PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Add link to the system

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem in
information retrieval. In particular, there are frameworks for estimating
relevance as a function of the content of the document and algorithms for
estimating relevance as a function of incoming links. However, further
specialization of these techniques is required to search a corpus of academic
papers. Academic papers are highly structured, lending additional weight to
matches which appear in important sections such as the title or abstract.
Contextual information changes the weight which should be contributed to cited
papers. Here we describe PubCrawl, a search engine built for the ACM Digital
Library. The system allows users to weight the relative importance of matches
in various sections of the documents. We also implement a version of PageRank
over the dataset. We evaluate the system in user studies.
\end{abstract}

@@

Here, we present PubCrawl, a system built to test ranking algorithms for
searching academic papers. The system searches over the complete ACM Digital
Library. We use Apache Lucene to index documents and estimate relevance and
PageRank to estimate importance. The system provides a web interface using the
Django web framework backed by a Postgres database. Users can input queries and
relative weights for matches in various sections of the document as well as the
PageRank.

@@

PubCrawl is an online search website for the ACM Digital Library built with the
Django web framework. It is backed by a Postgres database which stores metadata
(authors, venues, and citations) and a Lucene search index. The PubCrawl
interface allows users to submit search terms and assign relative weights to
title, abstract, and full text searches and PageRank. Figure \ref{interface}
shows a screenshot of the interface.

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\textwidth]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

However, because the data set is limited to ACM publications, the citation
graph is highly disconnected. Although the vast majority of the papers
(176,285) are contained in one component, in total there are 45,571 connected
components. Figure \ref{comp-size} shows the size distribution of these
components is heavily skewed. We take special consideration of component size
in our adaptation of the PageRank algorithm.

\begin{figure}[tb]
  \begin{center}
    \includegraphics[width=5in]{images/component-graph}
  \end{center}
  \caption{Distribution of component sizes in the citation graph}
  \label{comp-size}
\end{figure}

@@

@@

We implemented two ranking functions. The first only uses the full text score
and PageRank. The second uses an algorithm based on RankJoin
\cite{DBLP:conf/vldb/IlyasAE03} to combine lists of hits sorted by each of
title, abstract, and full text scores and PageRank. The algorithm maintains the
top $k$ hits seen so far. In each iteration, we pop the maximum element off of
the next list in round-robin order and hash it. When we encounter a duplicate,
we update the combined score and its position in the top $k$. The algorithm
terminates when the maximum possible score of unseen tuples is less than the
score of the $k$th hit.

@@

To evaluate the quality of PubCrawl results, we performed a preliminary user
study comparing the quality of PubCrawl results with those from Google Scholar,
Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
information about important papers on 6 topics from experts in the respective
areas. We then manually picked weights shown in Table \ref{weights} that gave
good results for all 6 topics.

\begin{table}[bt]
  \begin{center}
    \begin{tabular}{ll}
      Parameter & Weight\\
      \hline
      Title & 0.1\\
      Abstract & 0\\
      Document & 0.5\\
      PageRank & 1\\
    \end{tabular}
  \end{center}
  \caption{Manually optimized parameter settings for PubCrawl user study}
  \label{weights}
\end{table}

For 4 topics, we performed searches on the engines, generating lists of the top
10 ACM publications from each. We provided these lists to our experts who rated
each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
They also ranked the five lists in order of decreasing quality.

@@

Figure \ref{relevance1} shows the distribution of results grouped by ranks
assigned by users. PubCrawl produces a large number of moderately relevant
document but a low number both of highly relevant and not relevant results.
While we would ideally like to maximize the former, the low number of
irrelevant results suggests are method has a lower false positive rate.

Figure \ref{relevance2} shows the relevance ratio across all search engines.
Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
the number of Not relevant results. PubCrawl has relevance ratio comparable to
Google Scholar and Microsoft Academic Search. \citeseer, on the other hand, has
very poor relevance score since it produces a large number of irrelevant
results. ACM Digital Library has the largest number of relevant documents in
its results.

In Figure \ref{relevance3}, we show a total quality score which we define as $H
- N + .1 M$. We choose this metric to highly rank relevant results, penalize
for non-relevant results and factor in moderately relevant results.

Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine
based on the ranks assigned to each engine by our experts. A higher score
(scale of 5) indicates a better rank. On average, PubCrawl ranked as high as
the other engines except Google Scholar.

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance1}
\caption{Relevance of search results across all topics}
\label{relevance1}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance2}
\caption{Relevance ratio for each search engine}
\label{relevance2}
\end{figure}

@@

\subsection{Discussion}

Our preliminary user study only involved 4 topics and hence a larger study must
be undertaken to rigorously study the quality of results. We also observed
that: (1) quality of results depends heavily on the breadth of the search term
(a narrow search term produces better results), (2) ground truth wasn't always
clearly known, (3) ground-truth is subjective, (4) we had to discard a large
number of highly relevant but non-ACM publications. Furthermore, because we did
not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
weaker compared to other search engines. However, we did show that PubCrawl can
find relevant documents and effectively trade off PageRank and text indexing
scores.

@@

We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
studies.

>>>>

\documentclass[12pt]{article}
\usepackage{hyperref}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem in
information retrieval. In particular, there are frameworks for estimating
relevance as a function of the content of the document and algorithms for
estimating relevance as a function of incoming links. However, further
specialization of these techniques is required to search a corpus of academic
papers. Academic papers are highly structured, lending additional weight to
matches which appear in important sections such as the title or abstract.
Contextual information changes the weight which should be contributed to cited
papers. Here we describe PubCrawl, a search engine built for the ACM Digital
Library available at \url{http://saw.csail.mit.edu:9000}. The system allows
users to weight the relative importance of matches in various sections of the
documents. We also implement a version of PageRank over the dataset. We
evaluate the system in user studies and find it produces comparable results to
other search engines.
\end{abstract}

@@

@@

Here, we present PubCrawl, a new search engine for the ACM Digital Library
available at \url{http://saw.csail.mit.edu:9000}. The PubCrawl interface allows
users to submit search terms and assign relative weights to title, abstract,
and full text searches and PageRank. It uses the Django web framework for the
front-end interface and is backed by a Postgres database which stores metadata
(authors, venues, and citations) and a Lucene search index. Figure
\ref{interface} shows a screenshot of the interface.

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

However, because the data set is limited to ACM publications, the citation
graph is highly disconnected. Although the vast majority of the papers
(176,285) are contained in one component, in total there are 45,571 connected
components. Figure \ref{comp-size} shows the size distribution of these
components is heavily skewed. We take special consideration of component size
in our adaptation of the PageRank algorithm. Figure \ref{degree-dist} shows the
distribution of outdegrees in the largest component of the citation graph. As
expected, this distribution follows a power law.

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=5in]{images/component-graph}
  \end{center}
  \caption{Distribution of component sizes in the citation graph}
  \label{comp-size}
\end{figure}

\begin{figure}[p]
  \begin{center}
    \includegraphics{images/degree-graph}
  \end{center}
  \caption{Distribution of outdegrees in the largest component of the citation
    graph}
  \label{degree-dist}
\end{figure}

@@

Figure \ref{pagerank-dist} shows the distribution of PageRanks computed in that
component. This distribution also follows a power law, which is expected given
the distribution of outdegrees.

\begin{figure}[p]
  \begin{center}
    \includegraphics{images/pageranks}
  \end{center}
  \caption{Distribution of PageRanks in the largest component of the citation
    graph}
  \label{pagerank-dist}
\end{figure}

@@

We implemented two ranking functions. The first only uses the full text score
and PageRank. The second uses an algorithm based on RankJoin
\cite{DBLP:conf/vldb/IlyasAE03} to combine lists of hits sorted by each of
title, abstract, and full text scores and PageRank. The algorithm maintains the
top $k$ hits seen so far. In each iteration, we pop the maximum element off of
the next list in round-robin order and hash it. If the element can be joined
with an element seen from each of the other lists, then we update its score in
the top $k$. We special case the list of abstract scores because not all
documents have abstracts. The algorithm terminates when the maximum possible
score of unseen tuples is less than the score of the $k$th hit.

@@

To evaluate the quality of PubCrawl results, we performed a preliminary user
study comparing the quality of PubCrawl results with those from Google Scholar,
Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
information from experts about important papers on 6 topics: Provenance, stream
processing, Twitter, crowdsourcing, parallel databases, and NoSQL. We then
manually picked weights shown in Table \ref{weights} that gave good results for
all 6 topics.

\begin{table}[p]
  \begin{center}
    \begin{tabular}{ll}
      Parameter & Weight\\
      \hline
      Title & 0.1\\
      Abstract & 0.01\\
      Document & 0.5\\
      PageRank & 1\\
    \end{tabular}
  \end{center}
  \caption{Manually optimized parameter settings for PubCrawl user study}
  \label{weights}
\end{table}

For the user study, we threw out Provenance and NoSQL from the topics list.
Provenance did not have enough papers in the ACM data set; NoSQL is not a
commonly used term even in papers about such systems. For the remaining topics,
we performed searches on each of the engines, generating lists of the top 10
ACM publications from each. We provided these lists to our experts who rated
each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
They also ranked the five lists in order of decreasing quality.

@@

Table \ref{ratios} shows the distribution of relevance of results for each
search engine. Relevant results include both moderately and highly relevant
results. PubCrawl produces a comparable number of relevant documents to the
other search engines. We note \citeseer\ produces a large fraction of
irrelevant documents, which we suspect is due to its noisy data set.

However, PubCrawl produces a relatively low number of highly relevant results.
We believe there are several reasons this is the case. First, our citation
graph does not include non-ACM papers. This means relevant papers may not
necessarily have high PageRank in our system. Second, our Lucene text index
does not index $n$-grams, which reduces the quality of results for multiword
queries. Third, the Lucene scoring function based on VSM has been superseded by
other information retrieval metrics.

Figure \ref{relevance3} shows a quality score for each search engine, defined
as $H - N + .1 M$, where $H$ is the number of Highly Relevant papers, $M$ is
the number of Moderately Relevant papers, and $N$ is the number of Not Relevant
papers.

Figure \ref{rank1} shows the average rank assigned to an engine based on the
ranks assigned to each engine by our experts. A higher score (scale of 5)
indicates a better rank. On average, PubCrawl ranked as high as the other
engines except Google Scholar.

\begin{table}[p]
  \begin{center}
    \begin{tabular}{llll}
      Search Engine & Relevant & Highly Relevant & Not Relevant\\
      \hline
      Google Scholar & 0.9 & 0.45 & 0.1 \\
      Microsoft Academic Search & 0.875 & 0.275 & 0.125 \\
      \citeseer & 0.6 & 0.125 & 0.4 \\
      ACM Digital Library & 0.975 & 0.125 & 0.025 \\
      PubCrawl & 0.95 & 0.1 & 0.075 \\
    \end{tabular}
  \end{center}
  \caption{Ratio of results in each relevance category by search engine}
  \label{ratios}
\end{table}

@@

Our preliminary user study only involved 4 topics and hence a larger study must
be undertaken to rigorously study the quality of results. We also observed
that: (1) quality of results depends heavily on the breadth of the search term
(a narrow search term produces better results), (2) ground truth was not always
clearly known, (3) ground-truth is subjective, (4) we had to discard a large
number of highly relevant but non-ACM publications. Furthermore, because we did
not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
weaker compared to other search engines. However, we did show that PubCrawl can
find relevant documents and effectively trade off PageRank and text indexing
scores.

@@

We acknowledge James Cowling, Adam Marcus, Eugene Wu for their assistance with
the user studies and Sam Madden for his feedback on our methods.
